---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BioPathNet

<!-- badges: start -->
<!-- [![DOI](https://zenodo.org/badge/301042598.svg)](https://zenodo.org/badge/latestdoi/301042598) -->
[![GitHub issues](https://img.shields.io/github/issues/AliSajid/BioPathNet)](https://github.com/AliSajid/BioPathNet/issues)
[![GitHub forks](https://img.shields.io/github/forks/AliSajid/BioPathNet)](https://github.com/AliSajid/BioPathNet/network)
[![GitHub stars](https://img.shields.io/github/stars/AliSajid/BioPathNet)](https://github.com/AliSajid/BioPathNet/stargazers)

![GitHub release (latest SemVer including pre-releases)](https://img.shields.io/github/v/release/AliSajid/BioPathNet?include_prereleases&label=latest-release)
![GitHub release (latest SemVer)](https://img.shields.io/github/v/release/AliSajid/BioPathNet?label=latest-stable)
[![GitHub license](https://img.shields.io/github/license/AliSajid/BioPathNet)](https://github.com/AliSajid/BioPathNet/blob/main/LICENSE)

![GitHub language count](https://img.shields.io/github/languages/count/AliSajid/BioPathNet)
![GitHub top language](https://img.shields.io/github/languages/top/AliSajid/BioPathNet)
![Lines of code](https://img.shields.io/tokei/lines/github/AliSajid/BioPathNet)
![GitHub code size in bytes](https://img.shields.io/github/languages/code-size/AliSajid/BioPathNet)
![GitHub repo size](https://img.shields.io/github/repo-size/AliSajid/BioPathNet)
<!-- badges: end -->

The goal of BioPathNet is to ...

## Installation

You can install the released version of BioPathNet from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("BioPathNet")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AliSajid/BioPathNet")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(BioPathNet)
## basic example code
```
